### 2019-03-16 draft.tex
outline and definition begun

\documentclass[12pt]{article}
\usepackage[unicode=true]{hyperref}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath,amsthm,amsfonts,eucal}
\usepackage{graphicx}

\title{Applications of the Fresnel Integral}
\author{Jack Jones}
\date{March 17\th, 2019}

\newcommand\defbb[2]{\def#1{{\mathbb{#2}}}}
\newcommand\defbf[2]{\def#1{{\mathbf{#2}}}}
\newcommand\defcal[2]{\def#1{{\mathcal{#2}}}} % capital letters only
\newcommand\defrm[2]{\def#1{{\mathrm{#2}}}}
\newcommand\defsf[2]{\def#1{{\mathsf{#2}}}}
\newcommand\defvec[2]{\def#1{{\vec{#2}}}}
\def\vec{\mathbf}
\renewcommand\th[1][th]{$^{\text{#1}}$}

\let\C=\relax
\DeclareMathOperator\C{C} % C(x) := \int_0^x cos(t^2) \d{t}
\defbb\CC{C} % complex numbers
\defrm\ud{d}
\def\d#1{{\,\ud#1\,}}
\defrm\e{e}  % Euler's number
\DeclareMathOperator\erf{erf} % error function
\defsf\si{i} % \sqrt{-1}
\defbb\R{R}
\let\S=\relax
\DeclareMathOperator\S{S} % S(x) :=int_0^x sin(t^2) \d{t}

\begin{document}
\maketitle
\begin{abstract}

\end{abstract}
\clearpage

\section{Introduction}

\subsection{Definition of the Fresnel Integral}
The Fresnel integrals are two transcendental functions defined as follows
\begin{align}
  \S(x) &:= \int_0^x  \sin(\frac\pi2 t^2) \d{t}, \\
  \C(x) &:= \int_0^x \cos(\frac\pi2 t^2) \d{t}.
\end{align}
The difficulty is that these integrals cannot be computed with analytic means, i.e.~the functions are transcendenta \cite[p.195ff]{AS}.  This is in contrast to, e.g.
$$ \int_0^x (\sin t)^2 \d{t} = \frac12\int_0^x \left(1-\cos(2t)\right)\d{t} = \frac12x -\frac14\sin(2x).
$$

\subsection{Some simple history}
The Fresnel integral and the related Euler spiral were discovered multiple times during history.  One of the first occurrances is according to \cite{Lev08} by J. Bernoulli in 1694 where he defines a curve such that an ideal metal rod of this shape unwinds to a straight line when placed under load at the ends.  In 1744 Euler is able to describe the curve by a differential equation that also allows him to reformulate it as the Fresnel integral.  37 years later he is able to compute the limiting points ($t\to\pm\infty$) of the curve and integrals.  Fresnel rediscovers the curve in 1818 and successfully applies it to the diffraction on a slit \cite{Lev08}.  He is also able to compute a couple of values numerically.  In 1874 Cornu plotted the curve accurately and proposes it as a graphical means for computing diffraction problems.

\section{Properties}
\subsection{Basic properties}
The Fresnel integrals are odd, i.e.
\begin{align*}
	\S(-x) &= \S(x), & \C(-x) &= \C(x).
\end{align*}
\begin{proof}[Idea of proof]  The integrands $\sin(t^2)$ and $\cos(t^2)$ are even in $t$ and an anti-derivative $F(x)$ of an even function is odd if in addition $F(0)=0$.  The latter follows, because both integrals start at $t=0$.
\end{proof}

Their limits are
\[  \lim_{x\to\infty} \S(x) = 0.5\sqrt{\tfrac\pi2},\qquad  \lim_{x\to\infty} \C(x) = 0.5\sqrt{\tfrac\pi2}.
\]

Since the integrals cannot be computed by elementary analytic means, an alternative is to compute them with a power series.  Therefore we present the Taylor expansion as
\begin{align*}
  \S(x) &= \sqrt{\frac\pi2}\sum_{n\ge0} (-1)^nx^{4n+3}\frac{(\pi/2)^{2n+1}}{(2n+1)!(4n+3)}, \\
  \C(x) &= \sqrt{\frac\pi2}\sum_{n\ge0} (-1)^nx^{4n+1}\frac{(\pi/2)^{2n}}{(2n)!(4n+1)}.
\end{align*}
\begin{proof}[Idea of proof]  Start from the well known Taylor expansion of $\sin t = \sum_{n\ge0}$ $(-1)^n t^{2n+1}/(2n+1)!$ and $\cos t = \sum_{n\ge0} (-1)^nt^{2n}/(2n)!$, substitute $t\mapsto \tfrac\pi2 t^2$ and take the antiderivative for each summand.  The resulting series are $\S(t)$ and $\C(t)$, because the integral of an absolutely converging power series equals the absolutely converging power series of the integrals of the summands.
\end{proof}

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.5\textwidth]{Fresnel-Integrals-(Normalised).png}
	\caption{Fresnel integrals.  Taken from \cite[/Fresnel\_Integral]{wiki}.}
\end{figure}

\subsection{Other expressions}
The Fresnel integrals are closely related to the error function which is defined as follows
$$  \erf(x) := \int_{-x}^x \exp(-t^2) \d{t}.
$$
Also this function is analytic and can therefore be expanded to the whole complex plane.  Here the integral for fixed endpoints is independent of the path.

Now for the complex defintion of exponential function
\begin{align*}  \exp(x+\si y) &:= (\cos y +\si\sin y)\e^x
\intertext{we obtain}
  \C(z)+\si\S(z) &= \int_0^z \exp\left(\si\frac\pi2 t^2\right)\d{t} 
\intertext{Now we do a substitution in the complex plane as $t'=\sqrt{i}t$, i.e.~$\d{t'}=\frac{1+\si}{\sqrt{2}}\d{t}$ and obtain}
  &= \frac{1-\si}{\sqrt{2}}\int_0^{\frac{1+\si}{\sqrt{2}}} \exp(t^{\prime2}) \d{t'} = \frac12\,\frac{1-\si}{\sqrt2} \erf\left(\frac{1+\si}{\sqrt2}\,\frac\pi2 z\right).
\end{align*}
Therefore we can say that the Fresnel integrals are the real and imaginary part of the complex error function.

\section{Euler Spiral}
\cite{Lev08}  The Euler spiral is a curve in the complex plane that has curvature proportional to the arc length.  Here arc length is defined as
\[  s(T) := \int_0^T \sqrt{\d{x}^2+\d{y}^2}
\]  for some differentiable curve $(x(t),y(t))$ in the plane.  Note that the curve length is monotone increasing with the parameter $t$ of the curve.  For a nice curve, it is possible to reparametrize the cruve in the arc length, i.e.~$(x(s),y(s))$.

The curvature of a smooth curve is defined as 
\[  \kappa=\frac1R = \frac{\dot x\ddot y -\ddot x\dot y}{(\dot x)^2+(\dot y)^2}.
\]  Here $\dot{x}=\frac{\d{x}}{\d{t}}$ is the derivative by the parameter $t$ (and $\dot{y}$ that of $y(t)$ and $\ddot{x}$ the second derivative, correspondingly).  If we combine the coordinates to a complex number $z=x(t)+\si y(t)$ and reparametrize the curve in its arc length $z(s)$, then the curvature condition reads as
\[  z^{\prime\prime}\bar{z}' = \frac\si{R} = \si s.
\]  Here $z'=\frac{\d{z}}{\d{s}}$ is the derivative by the arc length.

\begin{itemize}\item The definition of Euler Spiral
\item The relation between Fresnel Integral and Euler Spiral
\end{itemize}

\section{Application of Fresnel Integral}
\subsection{Application using the Euler Spiral}
\cite{BH12}
Electromagnetic field intensity

\subsection{Further Applications}

\section{Conclusion}

\bibliographystyle{alphasorteprint}
\bibliography{bibliography.bib}
\nocite{AS, BE, Sim, Str, WW}  % TODO: place in text
\end{document}

### 2019-03-16 draft.tex
pictures for the intro

@@
 
-\let\C=\relax
-\DeclareMathOperator\C{C} % C(x) := \int_0^x cos(t^2) \d{t}
+%\let\C=\relax
+\DeclareMathOperator\Cee{C} % C(x) := \int_0^x cos(t^2) \d{t}
 \defbb\CC{C} % complex numbers
@@
 \defbb\R{R}
-\let\S=\relax
-\DeclareMathOperator\S{S} % S(x) :=int_0^x sin(t^2) \d{t}
+%\let\S=\relax
+\DeclareMathOperator\eS{S} % S(x) :=int_0^x sin(t^2) \d{t}
 
@@
 \begin{abstract}
-
+We will show the relation between Fresnel integrals, complex error function and Euler spiral.
+Furthermore we will show two applications of these, one to the optics of a finite slit, another one to \dots.
 \end{abstract}
@@
 \section{Introduction}
+The Fresnel integrals, complex error function and Euler spiral are three views of one and the same thing.
+They are widely used in physics, especially in optics but recently also in electronics.
+Let us begin this paper by introducing the Euler spiral.
+
+\begin{figure}[h!]
+    \centering
+	\includegraphics[height=5cm]{orange.jpg} \hfill
+	\includegraphics[height=5cm]{orangePeel.jpg}
+	\label{f:orangePeel}
+	\caption{Left: Peeling an orange in a spiral of height $1/N$.\\
+		Right: The flattened peel that resembles an Euler spiral.  Photos taken from \cite{BH12}.
+	}
+\end{figure}
+There are two standard ways of peeling an orange: either cut the skin along meridians, or cut it along a spiral.
+We consider here the second method, and study the shape of the spiral strip, when unfolded on a table.
+We derive a formula that describes the corresponding flattened-out spi- ral.
+Cutting the peel with progressively thinner strip widths, we obtain a sequence of increasingly long spirals.
+We show that, after rescaling, these spirals tends to a definite shape, known as the Eu- ler spiral.
+The Euler spiral has applications in many fields of science.
+In optics, the illumination intensity at a point behind a slit is computed from the distance between two points on the Euler spi- ral.
+The Euler spiral also provides optimal curva- ture for train tracks between a straight run and an upcoming bend.
+It is striking that it can be also obtained with an orange and a kitchen knife.
 
@@
 \begin{align}
-  \S(x) &:= \int_0^x  \sin(\frac\pi2 t^2) \d{t}, \\
-  \C(x) &:= \int_0^x \cos(\frac\pi2 t^2) \d{t}.
+  \eS(x) &:= \int_0^x  \sin\left(\frac\pi2 t^2\right) \d{t}, \\
+  \Cee(x) &:= \int_0^x \cos\left(\frac\pi2 t^2\right) \d{t}.
 \end{align}
-The difficulty is that these integrals cannot be computed with analytic means, i.e.~the functions are transcendenta \cite[p.195ff]{AS}.  This is in contrast to, e.g.
+The difficulty is that these integrals cannot be computed with analytic means, i.e.~the functions are transcendental \cite[p.195ff]{AS}.  This is in contrast to, e.g.
 $$ \int_0^x (\sin t)^2 \d{t} = \frac12\int_0^x \left(1-\cos(2t)\right)\d{t} = \frac12x -\frac14\sin(2x).
@@
 \begin{align*}
-	\S(-x) &= \S(x), & \C(-x) &= \C(x).
+	\eS(-x) &= \eS(x), & \Cee(-x) &= \Cee(x).
 \end{align*}
@@
 Their limits are
-\[  \lim_{x\to\infty} \S(x) = 0.5\sqrt{\tfrac\pi2},\qquad  \lim_{x\to\infty} \C(x) = 0.5\sqrt{\tfrac\pi2}.
+\[  \lim_{x\to\infty} \eS(x) = 0.5\sqrt{\tfrac\pi2},\qquad  \lim_{x\to\infty} \Cee(x) = 0.5\sqrt{\tfrac\pi2}.
 \]
@@
 \begin{align*}
-  \S(x) &= \sqrt{\frac\pi2}\sum_{n\ge0} (-1)^nx^{4n+3}\frac{(\pi/2)^{2n+1}}{(2n+1)!(4n+3)}, \\
-  \C(x) &= \sqrt{\frac\pi2}\sum_{n\ge0} (-1)^nx^{4n+1}\frac{(\pi/2)^{2n}}{(2n)!(4n+1)}.
+  \eS(x) &= \sqrt{\frac\pi2}\sum_{n\ge0} (-1)^nx^{4n+3}\frac{(\pi/2)^{2n+1}}{(2n+1)!(4n+3)}, \\
+  \Cee(x) &= \sqrt{\frac\pi2}\sum_{n\ge0} (-1)^nx^{4n+1}\frac{(\pi/2)^{2n}}{(2n)!(4n+1)}.
 \end{align*}
 \begin{proof}[Idea of proof]  Start from the well known Taylor expansion of $\sin t = \sum_{n\ge0}$ $(-1)^n t^{2n+1}/(2n+1)!$ and $\cos t = \sum_{n\ge0} (-1)^nt^{2n}/(2n)!$, substitute $t\mapsto \tfrac\pi2 t^2$ and take the antiderivative for each summand.
-The resulting series are $\S(t)$ and $\C(t)$, because the integral of an absolutely converging power series equals the absolutely converging power series of the integrals of the summands.
+The resulting series are $\eS(t)$ and $\Cee(t)$, because the integral of an absolutely converging power series equals the absolutely converging power series of the integrals of the summands.
 \end{proof}
@@
 \intertext{we obtain}
-  \C(z)+\si\S(z) &= \int_0^z \exp\left(\si\frac\pi2 t^2\right)\d{t} 
+  \Cee(z)+\si\eS(z) &= \int_0^z \exp\left(\si\frac\pi2 t^2\right)\d{t} 
 \intertext{Now we do a substitution in the complex plane as $t'=\sqrt{i}t$, i.e.~$\d{t'}=\frac{1+\si}{\sqrt{2}}\d{t}$ and obtain}

### 2019-03-16 draft.tex
pictures, including euler/cornu spiral.

@@
 	\label{f:orangePeel}
-	\caption{Left: Peeling an orange in a spiral of height $1/N$.\\
+	\caption{Left: Peeling an orange in a spiral of height $1/N$.
 		Right: The flattened peel that resembles an Euler spiral.  Photos taken from \cite{BH12}.
@@
 
+\begin{figure}[h!]
+	\centering
+	\includegraphics[height=5cm]{eulerSpiral.png}
+	\label{f:eulerSpiral}
+	\caption{Euler spiral.  Taken from \cite[/Fresnel\_integral\#/media/File:Cornu\_Spiral.svg]{wiki}.}
+\end{figure}
 \begin{itemize}\item The definition of Euler Spiral

### 2019-03-16 draft.tex
update 2

@@
+% !TeX spellcheck = en_US
 \documentclass[12pt]{article}
@@
 
-\title{Applications of the Fresnel Integral}
+\title{Applications of the Fresnel Integrals}
 \author{Jack Jones}
@@
 \renewcommand\th[1][th]{$^{\text{#1}}$}
+\newtheorem{thm}{T`heorem}
 
@@
 \def\d#1{{\,\ud#1\,}}
+\newcommand\udfrac[2]{\ensuremath{\frac{\ud#1}{\ud #2}}}
 \defrm\e{e}  % Euler's number
@@
 \begin{abstract}
-We will show the relation between Fresnel integrals, complex error function and Euler spiral.
-Furthermore we will show two applications of these, one to the optics of a finite slit, another one to \dots.
+
+The Euler spiral, defined by the linear relationship between curvature and arc length, is a beautiful and elegant plane curve. Its underlying mathematical equation is most
+commonly known as the Fresnel integrals.
+However, the Fresnel integrals and Euler spiral are  two views of one and the same thing.
+In this paper, we focus on Fresnel integral and study its properties and useful applications.
+In optics, the illumination
+intensity at a point behind a slit is computed from
+the distance between two points on the Euler spiral. The Euler spiral also provides optimal curvature for train tracks between a straight run and
+an upcoming bend
+
 \end{abstract}
@@
 \section{Introduction}
-The Fresnel integrals, complex error function and Euler spiral are three views of one and the same thing.
-They are widely used in physics, especially in optics but recently also in electronics.
-Let us begin this paper by introducing the Euler spiral.
+An Euler spiral is a curve whose curvature changes linearly with its curve length.
+Taking the example of peeling an orange with a kitchen knife, one can either cut the skin along meridians, or cut it along a spiral as the left image in Figure~\ref{f:orangePeel} shows.
+The red lines marked on the orange refer to the route one can follow to peel the orange.
+Later, if we unfold the spiral strip and flatten it on a table, we will see a long curve which is curved differently at different positions.
+Imagine that we will now cut the peel with progressively thinner strip widths, what we will obtain in the end is a long beautiful curve known as Euler spiral, as the left-side image in Figure~\ref{f:orangePeel} shows.
+According to Alfred Gray, Euler spiral is “one of the most elegant of all plane curves.” \cite{ASG17}
 
@@
 	\caption{Left: Peeling an orange in a spiral of height $1/N$.
-		Right: The flattened peel that resembles an Euler spiral.  Photos taken from \cite{BH12}.
+		Right: The flattened orange peel that resembles an Euler spiral.  Photos taken from \cite{BH12}.
 	}
 \end{figure}
-There are two standard ways of peeling an orange: either cut the skin along meridians, or cut it along a spiral.
-We consider here the second method, and study the shape of the spiral strip, when unfolded on a table.
-We derive a formula that describes the corresponding flattened-out spi- ral.
-Cutting the peel with progressively thinner strip widths, we obtain a sequence of increasingly long spirals.
-We show that, after rescaling, these spirals tends to a definite shape, known as the Eu- ler spiral.
-The Euler spiral has applications in many fields of science.
-In optics, the illumination intensity at a point behind a slit is computed from the distance between two points on the Euler spi- ral.
-The Euler spiral also provides optimal curva- ture for train tracks between a straight run and an upcoming bend.
-It is striking that it can be also obtained with an orange and a kitchen knife.
 
-\subsection{Definition of the Fresnel Integral}
-The Fresnel integrals are two transcendental functions defined as follows
+For a mathematician, an interesting question is whether there are any equations that can describe the corresponding shape of an Euler spiral.
+For this we consider the Fresnel integrals.
+These are defined as integrals over some elementary functions which can however not be integrated in elementary functions.
+These integrals occur naturally in the description of the optics of an illuminated slit (in Subsection~\ref{s:relation}).
+
+\subsection{Definition of Euler Spiral}
+The Euler Spiral is defined by the  linear relationship between curvature and arc length, was
+first proposed as a problem of elasticity by James Bernoulli, then solved accurately by Leonhard Euler \cite{Lev08}.
+The Euler spiral is a curve in the complex plane that has curvature proportional to the arc length.  Here the arc length $s(t)$ of a differentiable curve $(x(t),y(t))$ in the plane is defined by
+\[  \left(\udfrac{s}{t}\right)^2 := \left(\udfrac{x}{t}\right)^2 +\left(\udfrac{y}{t}\right)^2.
+\]  Note that the curve length is monotone increasing with the parameter $t$ of the curve.  For a nice curve, it is possible to rewrite the curve in the arc length, i.e.~$(x(s),y(s))$.
+
+The curvature of a smooth curve $\kappa$ can be defined as 
+\[  \kappa=\frac1R = x'y'' -x''y'
+\] if we assume that the curve is parameterized in the arc length $s$ \cite{BH12}.
+
+According to \cite{BH12} the peel of the orange can be approximated as:
+\begin{equation}
+  \kappa \sim s  \label{e:eulerSpiral}
+\end{equation}
+
+The question we want to answer is how to describe the solution of this differential equation explicitly.  Therefore we introduce the Fresnel integrals.
+
+\subsection{Definition of the Fresnel Integrals}
+The Fresnel sine and cosine integrals are represented by  $S(x)$ and $C(x)$, which are two integral functions that originate by applying the analysis of Fresnel diffraction phenomena.
+The mathematical equations are as follows:
+
 \begin{align}
 \eS(x) &:= \int_0^x  \sin\left(\frac\pi2 t^2\right) \d{t}, \\
-  \Cee(x) &:= \int_0^x \cos\left(\frac\pi2 t^2\right) \d{t}.
+\Cee(x) &:= \int_0^x \cos\left(\frac\pi2 t^2\right) \d{t},
 \end{align}
+where $x \ge 0$ is a real number and $t$ is a real variable. When x tends to infinite, $S=C=1/2$.
+
 The difficulty is that these integrals cannot be computed with analytic means, i.e.~the functions are transcendental \cite[p.195ff]{AS}.  This is in contrast to, e.g.
@@
 
-\subsection{Some simple history}
+\subsection{Mathematical history}
 The Fresnel integral and the related Euler spiral were discovered multiple times during history.
@@
 Bernoulli in 1694 where he defines a curve such that an ideal metal rod of this shape unwinds to a straight line when placed under load at the ends.
-In 1744 Euler is able to describe the curve by a differential equation that also allows him to reformulate it as the Fresnel integral.
+In 1744, Euler is able to describe the curve by a differential equation that also allows him to reformulate it as the Fresnel integral.
 37 years later he is able to compute the limiting points ($t\to\pm\infty$) of the curve and integrals.
@@
 
-\section{Properties}
+In the following sections, we will first describe the important properties of the Fresnel integrals followed by some important applications of it.
+
+\section{Properties of the Fresnel Integrals}
 \subsection{Basic properties}
@@
 	\includegraphics[width=0.5\textwidth]{Fresnel-Integrals-(Normalised).png}
-	\caption{Fresnel integrals.  Taken from \cite[/Fresnel\_Integral]{wiki}.}
+	\caption{Fresnel integrals \cite{wiki}.}
+\end{figure}
+
+\subsection{Relation to the Euler spiral}\label{s:relation}
+\begin{thm}  The curve $(x,y)=(C(t),S(t))$ is an Euler spiral.
+\end{thm}
+\begin{proof}  Let us start with showing that $t$ is the parameter of the arc length.  Consider therefore the derivatives
+\begin{align*}
+  C'(t) &= \frac\pi2\cos\left(\frac\pi2 t^2\right), &  
+  S'(t) &= \frac\pi2\sin\left(\frac\pi2 t^2\right), \\
+  C''(t) &= -\left(\frac\pi2\right)^2\sin\left(\frac\pi2 t^2\right)\cdot 2t, &
+  S''(t) ^= \left(\frac\pi2\right)^2\cos\left(\frac\pi2 t^2\right)\cdot 2t.
+\intertext{Then}
+  \left(\udfrac{s}{t}\right)^2 &= \left(\frac\pi2\right)^2 \sim t
+\end{align*}
+I.e.~up to a constant factor $t$ is the arc length of the curve.
+
+Let us now consider the curvature
+\begin{align*}
+  \kappa &= x'y''-x''y' \sim C'(t)S''(t)-C''(t)S'(t) = \frac{\pi}{2}2t \sim t
+\end{align*}
+\end{proof}
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{eulerSpiral.png}
+	\label{f:eulerSpiral}
+	\caption{Euler spiral $(x,y)=(\Cee(t),\eS(t))$ \cite{wiki}.}
 \end{figure}
@@
 
-Now for the complex defintion of exponential function
+Now for the complex definition of exponential function
 \begin{align*}  \exp(x+\si y) &:= (\cos y +\si\sin y)\e^x
@@
 
-\section{Euler Spiral}
-\cite{Lev08}  The Euler spiral is a curve in the complex plane that has curvature proportional to the arc length.  Here arc length is defined as
-\[  s(T) := \int_0^T \sqrt{\d{x}^2+\d{y}^2}
-\]  for some differentiable curve $(x(t),y(t))$ in the plane.
-Note that the curve length is monotone increasing with the parameter $t$ of the curve.
-For a nice curve, it is possible to reparametrize the cruve in the arc length, i.e.~$(x(s),y(s))$.
+\section{Applications of Fresnel Integral}
 
-The curvature of a smooth curve is defined as 
-\[  \kappa=\frac1R = \frac{\dot x\ddot y -\ddot x\dot y}{(\dot x)^2+(\dot y)^2}.
-\]  Here $\dot{x}=\frac{\d{x}}{\d{t}}$ is the derivative by the parameter $t$ (and $\dot{y}$ that of $y(t)$ and $\ddot{x}$ the second derivative, correspondingly).
-If we combine the coordinates to a complex number $z=x(t)+\si y(t)$ and reparametrize the curve in its arc length $z(s)$, then the curvature condition reads as
-\[  z^{\prime\prime}\bar{z}' = \frac\si{R} = \si s.
-\]  Here $z'=\frac{\d{z}}{\d{s}}$ is the derivative by the arc length.
+The error functions, Fresnel integrals, and related functions occur in a variety of physical applications.
+Fresnel integrals and Cornu’s spiral occurred originally in the analysis of the diffraction of light; see Born and Wolf (1999, §8.7).
+More recently, Cornu’s spiral appears in the design of highways and railroad tracks, robot trajectory planning, and computer-aided design; see Meek and Walton (1992).
 
-\begin{figure}[h!]
-	\centering
-	\includegraphics[height=5cm]{eulerSpiral.png}
-	\label{f:eulerSpiral}
-	\caption{Euler spiral.  Taken from \cite[/Fresnel\_integral\#/media/File:Cornu\_Spiral.svg]{wiki}.}
-\end{figure}
-\begin{itemize}\item The definition of Euler Spiral
-\item The relation between Fresnel Integral and Euler Spiral
-\end{itemize}
+In optics, the illumination intensity at a point behind a slit is computed from the distance between two points on the Euler spi- ral.
+The Euler spiral also provides optimal curva- ture for train tracks between a straight run and an upcoming bend.
+It is striking that it can be also obtained with an orange and a kitchen knife.
 
-\section{Application of Fresnel Integral}
+The Euler spiral has applications in many fields of science.
+
+The Euler spiral has applications in
+many fields of science. In optics, the illumination
+intensity at a point behind a slit is computed from
+the distance between two points on the Euler spiral. The Euler spiral also provides optimal curvature for train tracks between a straight run and
+an upcoming bend.
+
+Fraunhofer diffraction, asymptotics of Weyl sums, and railway and freeway constructions.
+
 \subsection{Application using the Euler Spiral}
@@
 Electromagnetic field intensity
+ in the physics of diffraction and is used in the theory of driving motorcar round a corner quickly.
 

### 2019-03-16 draft.tex
proofread §1,2

@@
 \usepackage{graphicx}
+\usepackage{placeins}
 
@@
 \renewcommand\th[1][th]{$^{\text{#1}}$}
-\newtheorem{thm}{T`heorem}
+\newtheorem*{thm}{Theorem}
 
-%\let\C=\relax
-\DeclareMathOperator\Cee{C} % C(x) := \int_0^x cos(t^2) \d{t}
+\let\C=\relax
+\DeclareMathOperator\C{C} % \C(x) := \int_0^x cos(\pi/2*t^2) \d{t}
 \defbb\CC{C} % complex numbers
@@
 \defbb\R{R}
-%\let\S=\relax
-\DeclareMathOperator\eS{S} % S(x) :=int_0^x sin(t^2) \d{t}
+\let\para=\S
+\let\S=\relax
+\DeclareMathOperator\S{S} % \S(x) := \int_0^x sin(\pi/2*t^2) \d{t}
 
-\begin{document}
+\begin{document}\def§{{\ensuremath{\para}}}
 \maketitle
@@
 
-The Euler spiral, defined by the linear relationship between curvature and arc length, is a beautiful and elegant plane curve. Its underlying mathematical equation is most
+The Euler spiral, that is defined by the linear relationship between curvature and arc length, is a beautiful and elegant plane curve. Its underlying mathematical equation is most
 commonly known as the Fresnel integrals.
@@
 \section{Introduction}
-An Euler spiral is a curve whose curvature changes linearly with its curve length.
-Taking the example of peeling an orange with a kitchen knife, one can either cut the skin along meridians, or cut it along a spiral as the left image in Figure~\ref{f:orangePeel} shows.
+An Euler spiral is a curve whose curvature changes linearly with its arc length.
+Taking the example of peeling an orange with a kitchen knife, one can either cut the skin along meridians, or cut it along a spiral as the left-hand image in Figure~\ref{f:orangePeel} shows.
 The red lines marked on the orange refer to the route one can follow to peel the orange.
 Later, if we unfold the spiral strip and flatten it on a table, we will see a long curve which is curved differently at different positions.
-Imagine that we will now cut the peel with progressively thinner strip widths, what we will obtain in the end is a long beautiful curve known as Euler spiral, as the left-side image in Figure~\ref{f:orangePeel} shows.
+Imagine that we will now cut the peel with progressively thinner strip widths, what we will obtain in the end is a long beautiful curve known as Euler spiral, as the right-hand image in Figure~\ref{f:orangePeel} shows.
 According to Alfred Gray, Euler spiral is “one of the most elegant of all plane curves.” \cite{ASG17}
@@
 These are defined as integrals over some elementary functions which can however not be integrated in elementary functions.
-These integrals occur naturally in the description of the optics of an illuminated slit (in Subsection~\ref{s:relation}).
+These integrals occur naturally in the description of the optics of an illuminated slit (see Subsection~\ref{s:relation}).
 
 \subsection{Definition of Euler Spiral}
-The Euler Spiral is defined by the  linear relationship between curvature and arc length, was
+The Euler Spiral is defined by the  linear relationship between curvature and arc length and was
 first proposed as a problem of elasticity by James Bernoulli, then solved accurately by Leonhard Euler \cite{Lev08}.
@@
 \[  \left(\udfrac{s}{t}\right)^2 := \left(\udfrac{x}{t}\right)^2 +\left(\udfrac{y}{t}\right)^2.
-\]  Note that the curve length is monotone increasing with the parameter $t$ of the curve.  For a nice curve, it is possible to rewrite the curve in the arc length, i.e.~$(x(s),y(s))$.
+\]  Note that the arc length is monotone increasing with the parameter $t$ of the curve.  For a nice curve, it is possible to rewrite the curve in the arc length, i.e.~$(x(s),y(s))$.
 
-The curvature of a smooth curve $\kappa$ can be defined as 
+The curvature $\kappa$ of a smooth curve can be defined as 
 \[  \kappa=\frac1R = x'y'' -x''y'
 \] if we assume that the curve is parameterized in the arc length $s$ \cite{BH12}.
+The meaning is that at a point $(x(s),y(s))$ we approximate the curve by a circle segment that touches in this point of at least second order.
+Then $R$ is the radius of this touching circle and $\kappa$ its inverse.
 
-According to \cite{BH12} the peel of the orange can be approximated as:
+According to \cite{BH12} the peel of the orange can be approximated as
 \begin{equation}
-  \kappa \sim s  \label{e:eulerSpiral}
-\end{equation}
+  \kappa \sim s  \label{e:eulerSpiral}.
+\end{equation}  This is the differential equation of the Euler curve.  The goal is to find all smooth curves $(x(s),y(s))$ whose curvature is in every point as described.
 
@@
 \subsection{Definition of the Fresnel Integrals}
-The Fresnel sine and cosine integrals are represented by  $S(x)$ and $C(x)$, which are two integral functions that originate by applying the analysis of Fresnel diffraction phenomena.
+The Fresnel sine and cosine integrals are represented by $\S(x)$ and $\C(x)$, which are two integral functions that originate by applying the analysis of Fresnel diffraction phenomena.
 The mathematical equations are as follows:
@@
 \begin{align}
-\eS(x) &:= \int_0^x  \sin\left(\frac\pi2 t^2\right) \d{t}, \\
-\Cee(x) &:= \int_0^x \cos\left(\frac\pi2 t^2\right) \d{t},
+  \S(x) &:= \int_0^x  \sin\left(\frac\pi2 t^2\right) \d{t}, \\
+  \C(x) &:= \int_0^x \cos\left(\frac\pi2 t^2\right) \d{t},
 \end{align}
-where $x \ge 0$ is a real number and $t$ is a real variable. When x tends to infinite, $S=C=1/2$.
+where $x$ is a real number and $t$ is a real variable. When $x$ tends to infinity, $\S=\C=1/2$.
 
@@
 37 years later he is able to compute the limiting points ($t\to\pm\infty$) of the curve and integrals.
-Fresnel rediscovers the curve in 1818 and successfully applies it to the diffraction on a slit \cite{Lev08}.
+Fresnel discovers the curve in 1818 independently and successfully applies it to the diffraction on a slit \cite{Lev08}.
 He is also able to compute a couple of values numerically.
@@
 \begin{align*}
-	\eS(-x) &= \eS(x), & \Cee(-x) &= \Cee(x).
+	\S(-x) &= \S(x), & \C(-x) &= \C(x).
 \end{align*}
@@
 Their limits are
-\[  \lim_{x\to\infty} \eS(x) = 0.5\sqrt{\tfrac\pi2},\qquad  \lim_{x\to\infty} \Cee(x) = 0.5\sqrt{\tfrac\pi2}.
+\[  \lim_{x\to\infty} \S(x) = 0.5,\qquad  \lim_{x\to\infty} \C(x) = 0.5.
 \]
@@
 \begin{align*}
-  \eS(x) &= \sqrt{\frac\pi2}\sum_{n\ge0} (-1)^nx^{4n+3}\frac{(\pi/2)^{2n+1}}{(2n+1)!(4n+3)}, \\
-  \Cee(x) &= \sqrt{\frac\pi2}\sum_{n\ge0} (-1)^nx^{4n+1}\frac{(\pi/2)^{2n}}{(2n)!(4n+1)}.
+  \S(x) &= \sqrt{\frac\pi2}\sum_{n\ge0} (-1)^nx^{4n+3}\frac{(\pi/2)^{2n+1}}{(2n+1)!(4n+3)}, \\
+  \C(x) &= \sqrt{\frac\pi2}\sum_{n\ge0} (-1)^nx^{4n+1}\frac{(\pi/2)^{2n}}{(2n)!(4n+1)}.
 \end{align*}
 \begin{proof}[Idea of proof]  Start from the well known Taylor expansion of $\sin t = \sum_{n\ge0}$ $(-1)^n t^{2n+1}/(2n+1)!$ and $\cos t = \sum_{n\ge0} (-1)^nt^{2n}/(2n)!$, substitute $t\mapsto \tfrac\pi2 t^2$ and take the antiderivative for each summand.
-The resulting series are $\eS(t)$ and $\Cee(t)$, because the integral of an absolutely converging power series equals the absolutely converging power series of the integrals of the summands.
+The resulting series are $\S(t)$ and $\C(t)$, because the integral of an absolutely converging power series equals the absolutely converging power series of the integrals of the summands.
 \end{proof}
@@
 
+\FloatBarrier
 \subsection{Relation to the Euler spiral}\label{s:relation}
-\begin{thm}  The curve $(x,y)=(C(t),S(t))$ is an Euler spiral.
+\begin{thm}  The curve $(x,y)=(\C(t),\S(t))$ is an Euler spiral.
 \end{thm}
@@
 \begin{align*}
-  C'(t) &= \frac\pi2\cos\left(\frac\pi2 t^2\right), &  
-  S'(t) &= \frac\pi2\sin\left(\frac\pi2 t^2\right), \\
-  C''(t) &= -\left(\frac\pi2\right)^2\sin\left(\frac\pi2 t^2\right)\cdot 2t, &
-  S''(t) ^= \left(\frac\pi2\right)^2\cos\left(\frac\pi2 t^2\right)\cdot 2t.
+  \C'(t) &= \cos\left(\frac\pi2 t^2\right), &  
+  \S'(t) &= \sin\left(\frac\pi2 t^2\right), \\
+  \C''(t) &= -\frac\pi2\sin\left(\frac\pi2 t^2\right)\cdot 2t, &
+  \S''(t) &= \frac\pi2\cos\left(\frac\pi2 t^2\right)\cdot 2t.
 \intertext{Then}
-  \left(\udfrac{s}{t}\right)^2 &= \left(\frac\pi2\right)^2 \sim t
+  \left(\udfrac{s}{t}\right)^2 &= (C'(t))^2+(S'(t))^2 = 1
 \end{align*}
-I.e.~up to a constant factor $t$ is the arc length of the curve.
+i.e.~$t$ is the arc length $s$ of the curve.
 
@@
 \begin{align*}
-  \kappa &= x'y''-x''y' \sim C'(t)S''(t)-C''(t)S'(t) = \frac{\pi}{2}2t \sim t
+  \kappa &= x'y''-x''y' = C'(t)S''(t)-C''(t)S'(t) = \frac{\pi}{2}2t \sim t
 \end{align*}
@@
 	\label{f:eulerSpiral}
-	\caption{Euler spiral $(x,y)=(\Cee(t),\eS(t))$ \cite{wiki}.}
+	\caption{Euler spiral $(x,y)=(\C(t),\S(t))$ \cite{wiki}.}
 \end{figure}
@@
 \intertext{we obtain}
-  \Cee(z)+\si\eS(z) &= \int_0^z \exp\left(\si\frac\pi2 t^2\right)\d{t} 
-\intertext{Now we do a substitution in the complex plane as $t'=\sqrt{i}t$, i.e.~$\d{t'}=\frac{1+\si}{\sqrt{2}}\d{t}$ and obtain}
-  &= \frac{1-\si}{\sqrt{2}}\int_0^{\frac{1+\si}{\sqrt{2}}} \exp(t^{\prime2}) \d{t'} = \frac12\,\frac{1-\si}{\sqrt2} \erf\left(\frac{1+\si}{\sqrt2}\,\frac\pi2 z\right).
+  \C(z)+\si\S(z) &= \int_0^z \exp\left(\si\frac\pi2 t^2\right)\d{t} 
+\intertext{Now we do a substitution in the complex plane as $t'=\sqrt{\si\frac\pi2}t$, i.e.~$\d{t'}=\frac{1+\si}{\sqrt{2}}\sqrt{\frac\pi2}\d{t}$ and obtain}
+  &= \frac{1-\si}{\sqrt{2}}\sqrt{\frac2\pi}\int_0^{\frac{1+\si}{\sqrt{2}}\sqrt{\frac\pi2}z} \exp(t^{\prime2}) \d{t'} = \frac12\sqrt{\frac2\pi}\,\frac{1-\si}{\sqrt2} \erf\left(\frac{1+\si}{\sqrt2}\,\sqrt{\frac\pi2} z\right).
 \end{align*}
@@
 \section{Applications of Fresnel Integral}
-
 The error functions, Fresnel integrals, and related functions occur in a variety of physical applications.

### 2019-03-16 draft.tex
application start

@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Fresnel-Integrals-(Normalised).png}
+	\includegraphics[width=0.4\textwidth]{Fresnel-Integrals-(Normalised).png}
 	\caption{Fresnel integrals \cite{wiki}.}
@@
 
-\section{Applications of Fresnel Integral}
-The error functions, Fresnel integrals, and related functions occur in a variety of physical applications.
-Fresnel integrals and Cornu’s spiral occurred originally in the analysis of the diffraction of light; see Born and Wolf (1999, §8.7).
-More recently, Cornu’s spiral appears in the design of highways and railroad tracks, robot trajectory planning, and computer-aided design; see Meek and Walton (1992).
+\section{Applications of the Fresnel Integrals}
+Fresnel Integrals and Euler spiral have applications in many fields of science.
+They occurred originally in the analysis of the diffraction of light.
+More recently, Euler spiral appears in the design of highways and railroad tracks, robot trajectory planning, and computer-aided design.
+In this section, we will describe two main applications of the Fresnel integrals in detail, namely the original Fresnel Diffraction and the railway construction.
 
-In optics, the illumination intensity at a point behind a slit is computed from the distance between two points on the Euler spi- ral.
-The Euler spiral also provides optimal curva- ture for train tracks between a straight run and an upcoming bend.
-It is striking that it can be also obtained with an orange and a kitchen knife.
-
-The Euler spiral has applications in many fields of science.
-
-The Euler spiral has applications in
-many fields of science. In optics, the illumination
-intensity at a point behind a slit is computed from
-the distance between two points on the Euler spiral. The Euler spiral also provides optimal curvature for train tracks between a straight run and
-an upcoming bend.
-
-Fraunhofer diffraction, asymptotics of Weyl sums, and railway and freeway constructions.
-
-\subsection{Application using the Euler Spiral}
+\subsection{Fresnel Diffraction}
 \cite{BH12}
 Electromagnetic field intensity
- in the physics of diffraction and is used in the theory of driving motorcar round a corner quickly.
+in the physics of diffraction
 
-\subsection{Further Applications}
+In optics, the illuminationintensity at a point behind a slit is computed from the distance between two points on the Euler spiral.
+
+\subsection{Railway  Construction}
+
+ is used in the theory of driving motorcar round a corner quickly.
+
+ The Euler spiral also provides optimal curvature for train tracks between a straight run and an upcoming bend.
 

### 2019-03-17 draft.tex
Fresnel diffraction

@@
 \subsection{Fresnel Diffraction}
-\cite{BH12}
-Electromagnetic field intensity
-in the physics of diffraction
+\defbf\E{E}
+\defbf\B{B}
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{opticalSetting.png} \\
+	% (2) \includegraphics[width=0.5\textwidth]{opticalParameters.png}
+	\label{f:FresnelDiffraction}
+	\caption{Fresnel diffraction after \cite[ch.~8.1]{Zim08}. Incoming parallel light waves from the left.  An aperture S' and an observation screen on the right in distance $D$.}
+\end{figure}
+According to \cite[ch.~7]{Zim08} the complexified electric field strength $\E$ at a point $P$ on the observation screen of a plane electromagnetic wave that went through an aperture $S'$ computes as
+\[  \E(P) = \B\iint  \frac1\rho \exp\left(\si(k\rho-\omega t)\right) \d{S'}
+\] where $\B$ determines the amplitude of the incoming wave,\\ $\rho=\sqrt{(x-x')^2+(y-y')^2+D^2}$ is the distance of the aperture point $S'$ from the observation point $P$.
+$k=\omega/c$ is the wave number, $\omega$ the frequency of the incoming monochromatic wave and $c>0$ the speed of light.
+In the Fresnel approximation we assume that $|x-x'|/D\ll 1$ and $|y-y'|/D\ll 1$, but will not assume that the aperture itself is small.
+Therefore we expand in the lowest orders of $(x-x')/D$ and $(y-y')/D$ and obtain
+\[  \E(P) \approx \B\frac{\exp\left(\si(kD-\omega t)\right)}{D} \iint \exp\left(\si(x'-x)^2k/2D +\si(y'-y)^2k/2D\right) \d{(x',y')}.
+\]  If we combine the constant coefficient as $\E_0$ and assume a rectangular aperture of size $[x_0,x_1]\times[y_0,y_1]$, we obtain
+\begin{align*}  \E(x,y) &\approx \E_0 \int_{u_0}^{u_1} \exp\left(\si\frac\pi2 u^2\right)\d{u} \int_{v_0}^{v_1} \exp\left(\si\frac\pi2 v^2\right) \d{v} \\
+  &= \E_0 \left[\C(u_1)+\si\S(u_1)-\C(u_0)-\si\S(u_0)\right] \left[\C(v_1)+\si\S(v_1)-\C(v_0)-\si\S(v_0)\right]
+\end{align*} where $u_k:=\sqrt{\frac2{D\lambda}}(x_k-x)$, $v_k:= \sqrt{\frac2{D\lambda}}(y_k-y)$ for $k=0,1$ \cite[Eqns.~(8.34a\&b)]{Zim08} and $\lambda=2\pi/k$ is the wave length.
+The intensity near a vertical edge results as
+\[  I(x):= |\E|^2 = \frac{I_0}{2} \left[\left(\frac12-\C(u_0)\right)^2+\left(\frac12-\S(u_0)\right)^2\right].
+\] See also \cite[Eqn.~(8.38)]{Zim08}.  This formula is the distance along the Euler spiral between the right point at $t=\infty$ and the left point at $t=u_0$.
 
-In optics, the illuminationintensity at a point behind a slit is computed from the distance between two points on the Euler spiral.
-
+\FloatBarrier 
 \subsection{Railway  Construction}

### 2019-03-17 draft.tex
the second app

--- 2019-03-16 draft.tex
@@
 
- is used in the theory of driving motorcar round a corner quickly.
+An object traveling on a circular path experiences a centripetral acceleration.
+The same happens when a train that travels on a straight path suddenly transitions to a tangential circular path.
+This sudden centripetal acceleration causes much discomfort for the driver as well as the passengers on the train.
 
- The Euler spiral also provides optimal curvature for train tracks between a straight run and an upcoming bend.
+In order to provide a smooth riding experience, much effort has been made in the history of railway construction.
+According to \cite{Lev08}, Mr.
+Gravatt was the first one who designed a sine curve around the year of 1828.
+Later by 1842, William Froude proposed to use a curve approximating the elastic curve, for the purpose of making the change of curvature by degree.
+In the year of 1880, Charles Crandall gives priority for the "true transition curve" to Ellis Holbrook in the Railroad Gazette.
+However, Arthur Talbot was among the first to approach the problem mathematically as he describes the problem and his solution in the introduction to "The Railway Transition Spiral" \cite{Tal99}:
+
+\begin{quotation}
+	A transition curve, or easement curve, as it is sometimes called, is a curve of varying radius
+	used to connect circular curves with tangents for the purpose of avoiding the shock and
+	disagreeable lurch of trains, due to the instant change of direction and also to the sudden
+	change from level to inclined track. The primary object of the transition curve, then, is to
+	effect smooth riding when the train is entering or leaving a curve.
+
+	The generally accepted requirement for a proper transition curve is that the degree-of-curve
+	shall increase gradually and uniformly from the point of tangent until the degree of the main
+	curve is reached, and that the super-elevation9
+	shall increase uniformly from zero at the
+	tangent to the full amount at the connection with the main curve and yet have at any point
+	the appropriate super-elevation for the curvature. In addition to this, an acceptable transition
+	curve must be so simple that the field work may be easily and rapidly done, and should be so
+	flexible that it may be adjusted to meet the varied requirements of problems in location and
+	construction.
+\end{quotation}
+
+Given the expression of centripetal acceleration $V^{2} / R$, the obvious solution is to provide an easement curve whose curvature, $1/R$, increases linearly with the traveled distance.
+This geometry is an Euler spiral.
+
+Unaware of the solution of the geometry by Leonhard Euler, Rankine cited the cubic curve (a polynomial curve of degree 3), which is an approximation of the Euler spiral for small angular changes in the same way that a parabola is an approximation to a circular curve.
+
+Marie Alfred Cornu (and later some civil engineers) also solved the calculus of Euler spiral independently.
+Euler spirals are now widely used in rail and highway engineering for providing a transition or an easement between a tangent and a horizontal circular curve.
 
 \section{Conclusion}
+The Euler spiral is a well known mathematical curve which can be constructed by peeling an orange around the spiral with a kitchen knife.
+Fresnel integrals are the mathematical equations that describe the Euler spiral.
+In this paper, we mainly study the properties of the Fresenal integrals and its two major applications: Fresnel Diffraction and railway transition curve construction.
 

### 2019-03-17 draft.tex
3.1 pictures
spellchecks

@@
 The Fresnel integral and the related Euler spiral were discovered multiple times during history.
-One of the first occurrances is according to \cite{Lev08} by J.
+One of the first occurrences is according to \cite{Lev08} by J.
 Bernoulli in 1694 where he defines a curve such that an ideal metal rod of this shape unwinds to a straight line when placed under load at the ends.
@@
 
-An object traveling on a circular path experiences a centripetral acceleration.
+An object traveling on a circular path experiences a centripetal acceleration.
 The same happens when a train that travels on a straight path suddenly transitions to a tangential circular path.
@@
 Later by 1842, William Froude proposed to use a curve approximating the elastic curve, for the purpose of making the change of curvature by degree.
-In the year of 1880, Charles Crandall gives priority for the "true transition curve" to Ellis Holbrook in the Railroad Gazette.
-However, Arthur Talbot was among the first to approach the problem mathematically as he describes the problem and his solution in the introduction to "The Railway Transition Spiral" \cite{Tal99}:
+In the year of 1880, Charles Crandall gives priority for the ``true transition curve'' to Ellis Holbrook in the Railroad Gazette.
+However, Arthur Talbot was among the first to approach the problem mathematically as he describes the problem and his solution in the introduction to ``The Railway Transition Spiral'' \cite{Tal99}:
 
@@
 
-Marie Alfred Cornu (and later some civil engineers) also solved the calculus of Euler spiral independently.
+Marie Alfred Cornu (and later some civil engineers) also solved the calculus of Euler spirals independently.
 Euler spirals are now widely used in rail and highway engineering for providing a transition or an easement between a tangent and a horizontal circular curve.
@@
 \bibliography{bibliography.bib}
-\nocite{AS, BE, Sim, Str, WW}  % TODO: place in text
+%\nocite{AS, BE, Sim, Str, WW}  % TODO: place in text
 \end{document}

### 2019-03-17 draft.tex
spell checks

@@
 However, the Fresnel integrals and Euler spiral are  two views of one and the same thing.
-In this paper, we focus on Fresnel integral and study its properties and useful applications.
-In optics, the illumination
-intensity at a point behind a slit is computed from
-the distance between two points on the Euler spiral. The Euler spiral also provides optimal curvature for train tracks between a straight run and
-an upcoming bend
+In this paper, we focus on the Fresnel integrals and study its properties and useful applications.
+In optics, the illumination intensity at a point behind a straight edge is computed from the distance between two points on the Euler spiral.
+The Euler spiral also provides optimal curvature for train tracks between a straight run and an upcoming bend.
 
@@
 These are defined as integrals over some elementary functions which can however not be integrated in elementary functions.
-These integrals occur naturally in the description of the optics of an illuminated slit (see Subsection~\ref{s:relation}).
+These integrals occur naturally in the description of the optics of an illuminated straight edge (see Subsection~\ref{s:relation}).
 
@@
 \] where $\B$ determines the amplitude of the incoming wave,\\ $\rho=\sqrt{(x-x')^2+(y-y')^2+D^2}$ is the distance of the aperture point $S'$ from the observation point $P$.
-$k=\omega/c$ is the wave number, $\omega$ the frequency of the incoming monochromatic wave and $c>0$ the speed of light.
+$k=\omega/c$ is the wave number, $\omega>0$ the frequency of the incoming monochromatic wave and $c>0$ the speed of light.
 In the Fresnel approximation we assume that $|x-x'|/D\ll 1$ and $|y-y'|/D\ll 1$, but will not assume that the aperture itself is small.
@@
 \section{Conclusion}
-The Euler spiral is a well known mathematical curve which can be constructed by peeling an orange around the spiral with a kitchen knife.
+The Euler spiral is a well known mathematical curve which can be constructed by peeling an orange along a spiral with a kitchen knife.
 Fresnel integrals are the mathematical equations that describe the Euler spiral.
-In this paper, we mainly study the properties of the Fresenal integrals and its two major applications: Fresnel Diffraction and railway transition curve construction.
+In this paper, we mainly studied the properties of the Fresnel integrals and its two major applications: Fresnel Diffraction and railway transition curve construction.
 

### 2019-03-17 draft.tex
spell check

@@
 	shall increase gradually and uniformly from the point of tangent until the degree of the main
-	curve is reached, and that the super-elevation9
-	shall increase uniformly from zero at the
+	curve is reached, and that the super-elevation shall increase uniformly from zero at the
 	tangent to the full amount at the connection with the main curve and yet have at any point
@@
 \bibliography{bibliography.bib}
-%\nocite{AS, BE, Sim, Str, WW}  % TODO: place in text
 \end{document}

### 2019-03-17 draft.tex
more words

@@
 \section{Introduction}
-An Euler spiral is a curve whose curvature changes linearly with its arc length.
-Taking the example of peeling an orange with a kitchen knife, one can either cut the skin along meridians, or cut it along a spiral as the left-hand image in Figure~\ref{f:orangePeel} shows.
+An Euler spiral is a famous curve whose curvature changes proportional to  its arc length.
+Taking the example of peeling an orange with a kitchen knife, one can either cut the skin vertically, or cut it along a spiral as the left-hand image in Figure~\ref{f:orangePeel} shows.
 The red lines marked on the orange refer to the route one can follow to peel the orange.
 Later, if we unfold the spiral strip and flatten it on a table, we will see a long curve which is curved differently at different positions.
-Imagine that we will now cut the peel with progressively thinner strip widths, what we will obtain in the end is a long beautiful curve known as Euler spiral, as the right-hand image in Figure~\ref{f:orangePeel} shows.
+Imagine that we will now cut the peel with progressively thinner width of the strip, what we will obtain in the end is a long beautiful curve known as Euler spiral, as the right-hand image in Figure~\ref{f:orangePeel} shows.
 According to Alfred Gray, Euler spiral is “one of the most elegant of all plane curves.” \cite{ASG17}
@@
 These are defined as integrals over some elementary functions which can however not be integrated in elementary functions.
-These integrals occur naturally in the description of the optics of an illuminated straight edge (see Subsection~\ref{s:relation}).
+These integrals occur naturally in the description of the optics of an illuminated straight edge (see Subsection~\ref{s:app1}).
 
 \subsection{Definition of Euler Spiral}
-The Euler Spiral is defined by the  linear relationship between curvature and arc length and was
+The Euler Spiral, defined by the  linear relationship between curvature and arc length, was
 first proposed as a problem of elasticity by James Bernoulli, then solved accurately by Leonhard Euler \cite{Lev08}.
@@
 \subsection{Mathematical history}
-The Fresnel integral and the related Euler spiral were discovered multiple times during history.
-One of the first occurrences is according to \cite{Lev08} by J.
-Bernoulli in 1694 where he defines a curve such that an ideal metal rod of this shape unwinds to a straight line when placed under load at the ends.
-In 1744, Euler is able to describe the curve by a differential equation that also allows him to reformulate it as the Fresnel integral.
-37 years later he is able to compute the limiting points ($t\to\pm\infty$) of the curve and integrals.
-Fresnel discovers the curve in 1818 independently and successfully applies it to the diffraction on a slit \cite{Lev08}.
+If we trace the history of the Euler spiral and Fresnel integrals, we will find it under different authors, e.g.~Fresnel, Cornu, Euler etc.
+This is because of the long history that Fresnel integral and the related Euler spiral have already left behind.
+They were discovered multiple times and under varying names during history.
+One of the first occurrences is according to \cite{Lev08} by the French physicist J.
+Bernoulli in 1694.
+Bernoulli approached many problems in elasticity theory at that time.
+One of them is a curve such that an ideal metal rod of this shape unwinds to a straight line when placed under load at the ends.
+He tried to find an explicit mathematical description of that curve, but it turned out that it is not that easy to do so at that time.
+In 1744, Swiss physicist and mathematician L.
+Euler is able to describe the same curve by a differential equation.
+This allows him to formulate a solution with integrals, namely what will later be called the Fresnel integrals.
+37 years later, he computes the limiting points ($t\to\pm\infty$) of the curve and integrals which are $(\pm1/2,\pm1/2)$.
+In 1818, the French A.J.
+Fresnel who deals with many problems in wave optics and is unaware of the earlier results by Bernoulli and Euler discovers the Euler spiral independently and successfully applies it to the diffraction on a slit \cite{Lev08}.
 He is also able to compute a couple of values numerically.
-In 1874 Cornu plotted the curve accurately and proposes it as a graphical means for computing diffraction problems.
-
-In the following sections, we will first describe the important properties of the Fresnel integrals followed by some important applications of it.
+With this finding he is able to establish the success of wave optics over particle optics which describes light as a transversal wave as opposed to the older idea by Newton who described light as consisting of particles.
+In 1874 the French physicist M.A.
+Cornu followed similar ideas as Fresnel and is able to plot the curve accurately and proposes it as a graphical means for computing diffraction problems.
+For that reason the Euler spiral is often also called Cornu spiral.
 
 \section{Properties of the Fresnel Integrals}
+The Fresnel integrals have many interesting mathematical properties. In this section, we will present some of them. 
 \subsection{Basic properties}
@@
 
-\subsection{Fresnel Diffraction}
+\subsection{Fresnel Diffraction}\label{s:app1}
 \defbf\E{E}

### 2019-03-17 draft.tex
formatted properties

@@
 
-The Euler spiral, that is defined by the linear relationship between curvature and arc length, is a beautiful and elegant plane curve. Its underlying mathematical equation is most
+The Euler spiral, that is defined by a linear relationship between curvature and arc length, is a beautiful and elegant plane curve. Its underlying mathematical equation is most
 commonly known as the Fresnel integrals.
@@
 Imagine that we will now cut the peel with progressively thinner width of the strip, what we will obtain in the end is a long beautiful curve known as Euler spiral, as the right-hand image in Figure~\ref{f:orangePeel} shows.
-According to Alfred Gray, Euler spiral is “one of the most elegant of all plane curves.” \cite{ASG17}
+According to Alfred Gray, Euler spiral is ``one of the most elegant of all plane curves.'' \cite{ASG17}
 
@@
 \subsection{Definition of the Fresnel Integrals}
-The Fresnel sine and cosine integrals are represented by $\S(x)$ and $\C(x)$, which are two integral functions that originate by applying the analysis of Fresnel diffraction phenomena.
+The Fresnel sine and cosine integrals are represented as $\S(x)$ and $\C(x)$.
+They are two integral functions that originate by applying the analysis of Fresnel diffraction phenomena.
 The mathematical equations are as follows:
@@
 \begin{align}
-  \S(x) &:= \int_0^x  \sin\left(\frac\pi2 t^2\right) \d{t}, \\
-  \C(x) &:= \int_0^x \cos\left(\frac\pi2 t^2\right) \d{t},
+  \S(x) &:= \int_0^x  \sin\left(\frac\pi2 t^2\right) \d{t}, \label{e:FresnelS}\\
+  \C(x) &:= \int_0^x \cos\left(\frac\pi2 t^2\right) \d{t}, \label{e:FresnelC}
 \end{align}
-where $x$ is a real number and $t$ is a real variable. When $x$ tends to infinity, $\S=\C=1/2$.
-
-The difficulty is that these integrals cannot be computed with analytic means, i.e.~the functions are transcendental \cite[p.195ff]{AS}.  This is in contrast to, e.g.
+where $x$ is a real number and $t$ is a real variable.
+The coefficient $\pi/2$ is just for normalization.
+In particular, when $x$ tends to infinity, $\S=\C=1/2$.
+The important property is that the integrand is a trigonometric function in the square of the integration variable.
+The result is that these integrals cannot be computed with analytic means, i.e.~the functions are transcendental \cite[p.195ff]{AS}.
+This is in contrast to, e.g.
 $$ \int_0^x (\sin t)^2 \d{t} = \frac12\int_0^x \left(1-\cos(2t)\right)\d{t} = \frac12x -\frac14\sin(2x).
-$$
+$$  The first step comes from the double angle formula $\cos(2t)=1-2(\sin t)^2$ \cite{AS}.  There is however no square angle formula, i.e.~anything related to $\cos(t^2)$.
 
 \subsection{Mathematical history}
-If we trace the history of the Euler spiral and Fresnel integrals, we will find it under different authors, e.g.~Fresnel, Cornu, Euler etc.
+If we trace the history of the Euler spiral and Fresnel integrals, we will find it under different authors, e.g.~Fresnel, Euler, Cornu and others.
 This is because of the long history that Fresnel integral and the related Euler spiral have already left behind.
@@
 \subsection{Basic properties}
-The Fresnel integrals are odd, i.e.
+\begin{enumerate}
+\item The Fresnel integrals are odd, i.e.
 \begin{align*}
@@
 \end{proof}
+In particular this implies $\C(0)=0=\S(0)$.
 
-Their limits are
-\[  \lim_{x\to\infty} \S(x) = 0.5,\qquad  \lim_{x\to\infty} \C(x) = 0.5.
+\item Their limits are according to \cite{AS}
+\[  \lim_{x\to\pm\infty} \S(x) = \pm0.5,\qquad  \lim_{x\to\pm\infty} \C(x) = \pm0.5.
 \]
 
-Since the integrals cannot be computed by elementary analytic means, an alternative is to compute them with a power series.  Therefore we present the Taylor expansion as
+\item Since the integrals cannot be computed by elementary analytic means, an alternative is to compute them via power series.  Therefore we present the Taylor expansion as
 \begin{align*}
@@
 \end{proof}
+\item From the power series it follows that the Fresnel integrals are analytic on the whole complex plane.  In particular they are entire complex functions.
 
+\item With these power series it is possible to draw the Fresnel integrals for real arguments Figure~\ref{f:graphFresnelIntegrals}.
+\end{enumerate}
 \begin{figure}[h!]
@@
 	\includegraphics[width=0.4\textwidth]{Fresnel-Integrals-(Normalised).png}
+	\label{f:graphFresnelIntegrals}
 	\caption{Fresnel integrals \cite{wiki}.}
@@
 \subsection{Relation to the Euler spiral}\label{s:relation}
+We will now formulate a major relation between the Fresnel integrals and the Euler spiral.
+This was first observed by Euler in 1744.
+Euler derived this property by constructing the solution of the differential equation \eqref{e:eulerSpiral} where he obtained what was later called Fresnel integrals \eqref{e:FresnelS} and \eqref{e:FresnelC}.
 \begin{thm}  The curve $(x,y)=(\C(t),\S(t))$ is an Euler spiral.
 \end{thm}
-\begin{proof}  Let us start with showing that $t$ is the parameter of the arc length.  Consider therefore the derivatives
+\begin{proof}  Let us start by showing that $t$ is the parameter of the arc length.  Consider therefore the derivatives
 \begin{align*}
@@
   \kappa &= x'y''-x''y' = C'(t)S''(t)-C''(t)S'(t) = \frac{\pi}{2}2t \sim t
-\end{align*}
+\end{align*}  This completes the proof of the theorem.
 \end{proof}
@@
 $$
-Also this function is analytic and can therefore be expanded to the whole complex plane.  Here the integral for fixed endpoints is independent of the path.
+Also this function is analytic and can therefore be expanded to the whole complex plane.  Here the integral for fixed endpoints is independent of the path by Cauchy's theorem \cite[p.~205]{Rudin}.
 
 Now for the complex definition of exponential function
-\begin{align*}  \exp(x+\si y) &:= (\cos y +\si\sin y)\e^x
+\begin{align}  \exp(x+\si y) &:= (\cos y +\si\sin y)\e^x \label{e:CFresnel}
 \intertext{we obtain}
   \C(z)+\si\S(z) &= \int_0^z \exp\left(\si\frac\pi2 t^2\right)\d{t} 
-\intertext{Now we do a substitution in the complex plane as $t'=\sqrt{\si\frac\pi2}t$, i.e.~$\d{t'}=\frac{1+\si}{\sqrt{2}}\sqrt{\frac\pi2}\d{t}$ and obtain}
+\intertext{Here we do a substitution in the complex plane as $t'=\sqrt{\si\frac\pi2}t$, i.e.~$\d{t'}=\frac{1+\si}{\sqrt{2}}\sqrt{\frac\pi2}\d{t}$ and obtain}
   &= \frac{1-\si}{\sqrt{2}}\sqrt{\frac2\pi}\int_0^{\frac{1+\si}{\sqrt{2}}\sqrt{\frac\pi2}z} \exp(t^{\prime2}) \d{t'} = \frac12\sqrt{\frac2\pi}\,\frac{1-\si}{\sqrt2} \erf\left(\frac{1+\si}{\sqrt2}\,\sqrt{\frac\pi2} z\right).
-\end{align*}
+\nonumber
+\end{align}
 Therefore we can say that the Fresnel integrals are the real and imaginary part of the complex error function.
@@
 \end{figure}
-According to \cite[ch.~7]{Zim08} the complexified electric field strength $\E$ at a point $P$ on the observation screen of a plane electromagnetic wave that went through an aperture $S'$ computes as
+Consider an optical construction as in Figure~\ref{f:FresnelDiffraction}: A monochromatic plane light wave of amplitude $\B$ and frequency $\omega>0$ enters from the left through a plane aperture $S'$.
+The light that emerges from the aperture travels a horizontal distance $D$ until it hits an observation screen.
+Mathematically this is described as follows \cite[ch.~7]{Zim08}.
+The electric field strength $\E$ at a point $P$ with coordinates $(x,y,D)$ on the observation screen computes as
 \[  \E(P) = \B\iint  \frac1\rho \exp\left(\si(k\rho-\omega t)\right) \d{S'}
-\] where $\B$ determines the amplitude of the incoming wave,\\ $\rho=\sqrt{(x-x')^2+(y-y')^2+D^2}$ is the distance of the aperture point $S'$ from the observation point $P$.
-$k=\omega/c$ is the wave number, $\omega>0$ the frequency of the incoming monochromatic wave and $c>0$ the speed of light.
-In the Fresnel approximation we assume that $|x-x'|/D\ll 1$ and $|y-y'|/D\ll 1$, but will not assume that the aperture itself is small.
+\] where $\rho=\sqrt{(x-x')^2+(y-y')^2+D^2}$ is the distance of the aperture point $S'$ with coordinates $(x',y',0)$ from the observation point $P$.
+$k=\omega/c$ is the wave number and $c>0$ the speed of light.
+In the Fresnel approximation we assume that $|x-x'|/D\ll 1$ and $|y-y'|/D\ll 1$, but will not assume that the aperture itself is small compared to the wave length.
 Therefore we expand in the lowest orders of $(x-x')/D$ and $(y-y')/D$ and obtain
@@
 \]  If we combine the constant coefficient as $\E_0$ and assume a rectangular aperture of size $[x_0,x_1]\times[y_0,y_1]$, we obtain
-\begin{align*}  \E(x,y) &\approx \E_0 \int_{u_0}^{u_1} \exp\left(\si\frac\pi2 u^2\right)\d{u} \int_{v_0}^{v_1} \exp\left(\si\frac\pi2 v^2\right) \d{v} \\
+\begin{align*}  \E(x,y) &\approx \E_0 \int_{u_0}^{u_1} \exp\left(\si\frac\pi2 u^2\right)\d{u} \int_{v_0}^{v_1} \exp\left(\si\frac\pi2 v^2\right) \d{v} 
+\intertext{Here we see that integrals of the complex error function arise.  According to \eqref{e:CFresnel} we can compute that with the Fresnel integrals as}
   &= \E_0 \left[\C(u_1)+\si\S(u_1)-\C(u_0)-\si\S(u_0)\right] \left[\C(v_1)+\si\S(v_1)-\C(v_0)-\si\S(v_0)\right]
 \end{align*} where $u_k:=\sqrt{\frac2{D\lambda}}(x_k-x)$, $v_k:= \sqrt{\frac2{D\lambda}}(y_k-y)$ for $k=0,1$ \cite[Eqns.~(8.34a\&b)]{Zim08} and $\lambda=2\pi/k$ is the wave length.
-The intensity near a vertical edge results as
+The intensity near a vertical edge ($y_0=-\infty$, $y_1=\infty$) results as
 \[  I(x):= |\E|^2 = \frac{I_0}{2} \left[\left(\frac12-\C(u_0)\right)^2+\left(\frac12-\S(u_0)\right)^2\right].
 \] See also \cite[Eqn.~(8.38)]{Zim08}.  This formula is the distance along the Euler spiral between the right point at $t=\infty$ and the left point at $t=u_0$.
+
+Therefore Cornu proposed to use the Euler spiral as a nomogram to do intensity computations in wave optics.
 

### 2019-03-17 draft.tex
2.1 added explanations

@@
 \end{proof}
-In particular this implies $\C(0)=0=\S(0)$.
+This means that the full graphs of $\S$ and $\C$ are point symmetric at the origin.  It is therefore enough to plot them for positive arguments.  In particular this implies $\C(0)=0=\S(0)$.
 
@@
 \[  \lim_{x\to\pm\infty} \S(x) = \pm0.5,\qquad  \lim_{x\to\pm\infty} \C(x) = \pm0.5.
-\]
+\]  Euler was first able to compute these limits from an analysis of the Fresnel integrals.
+From the formulation as integral it is not obvious that the improper integrals (with unbounded domain) converge to a finite value of $1/2$.
+However if we note that the integrand is oscillating with increasing amplitude ($\sin(t^2)=\sin(\omega t)$ for $\omega(t)=t$ increasing, and the analogue for $\cos(t^2)$), then it becomes plausible that the alternating positive and negative contributions from $t^2=k\pi$ to $t^2=(k+1)\pi$ (i.e.~lengths of the intervals $\sqrt{(k+1)\pi}-\sqrt{k\pi}$ for $k=0,1,2,\dots$) become smaller and smaller, asymptotically approaching 0.
+By Leibniz criterion the whole integral should thus converge.
 
@@
 \end{proof}
-\item From the power series it follows that the Fresnel integrals are analytic on the whole complex plane.  In particular they are entire complex functions.
+In order to compute approximate numerical values for particular finite arguments, we would now sum up the Taylor series up to a certain degree $n$ such that the following term (for $n+1$ which is of the order of the error) is small compared to the required precision.
+Unfortunately this means that we need to add more terms for larger arguments $x$.
+The formulas are therefore not very helpful to compute the limit $x\to\pm\infty$.
+
+\item From the power series it follows that the Fresnel integrals are analytic on the whole complex plane.
+In particular they are entire complex functions.
+This allows us to use the full machinery of complex analysis to discuss further properties of the integrals.
 
 \item With these power series it is possible to draw the Fresnel integrals for real arguments Figure~\ref{f:graphFresnelIntegrals}.
+Similar to the sine and cosine functions, the Fresnel integrals are oscillating.
+However the distance between consecutive local maxima (or also consecutive local minima) are constantly decreasing.
+This is as we already argued under the limit $x\to\infty$, because the integrands are alternatingly positive and negative for intervals of decreasing length.
 \end{enumerate}
@@
 \end{proof}
+
+This theorem establishes two things.
+First, the Fresnel integrals are particular solutions of the Euler spiral \eqref{e:eulerSpiral}.
+This is particularly helpful for engineers, because in practical applications it is necessary to draw and compute the shape of the Euler spiral.
+
+Secondly, the Euler spiral \eqref{e:eulerSpiral} has a solution for the whole parameter range $t\in\R$.
+This property is not obvious, because usual existence and uniqueness theorems for ordinary differential equations \cite[Picard--Lindeloff theorem]{sim} either only work for linear differential equations or only state local existence and uniqueness.
 

### 2019-03-17 draft.tex
rewritten 3.2

@@
 \subsection{Railway  Construction}
-
-An object traveling on a circular path experiences a centripetal acceleration.
-The same happens when a train that travels on a straight path suddenly transitions to a tangential circular path.
-This sudden centripetal acceleration causes much discomfort for the driver as well as the passengers on the train.
-
-In order to provide a smooth riding experience, much effort has been made in the history of railway construction.
+An object traveling at speed $v$ on a circular path of radius $R$ experiences a centripetal acceleration $a$ as
+$$  a = v^2/R.
+$$ When a vehicle that travels on a straight path suddenly transitions to a circular path, then the acceleration sensed by the passengers suddenly changes from $0$ for the straight segment ($1/R=0$) to some positive value ($a>0$, because $1/R>0$).
+This sudden centripetal acceleration gives much discomfort for the driver as well as the passengers on the vehicle.
+The effect is small when, e.g.~the first trains traveled at quite low speeds, but becomes much stronger when the speed increases ($a\sim v^2$).
+Therefore increased speeds of trains triggered the quest for better designed tracks.
 According to \cite{Lev08}, Mr.
-Gravatt was the first one who designed a sine curve around the year of 1828.
-Later by 1842, William Froude proposed to use a curve approximating the elastic curve, for the purpose of making the change of curvature by degree.
-In the year of 1880, Charles Crandall gives priority for the ``true transition curve'' to Ellis Holbrook in the Railroad Gazette.
-However, Arthur Talbot was among the first to approach the problem mathematically as he describes the problem and his solution in the introduction to ``The Railway Transition Spiral'' \cite{Tal99}:
+Gravatt was the first one who choose a sine curve for the transition from a straight segment to a curve around the year of 1828.
+Later in 1842, William Froude proposed the use of an elastic curve in order to make the change of curvature more smooth.
+In 1880, Charles Crandall asks for priority for the ``true transition curve'' in the Railroad Gazette.
+The problem is officially on to Ellis Holbrook to be solved, however, Arthur Talbot was among the first to approach the problem mathematically.
+He describes the problem and his solution in the introduction to ``The Railway Transition Spiral'' \cite{Tal99} which we quote here for being pronounced:
 
 \begin{quotation}
-	A transition curve, or easement curve, as it is sometimes called, is a curve of varying radius
-	used to connect circular curves with tangents for the purpose of avoiding the shock and
-	disagreeable lurch of trains, due to the instant change of direction and also to the sudden
-	change from level to inclined track. The primary object of the transition curve, then, is to
-	effect smooth riding when the train is entering or leaving a curve.
+	A transition curve, or easement curve, as it is sometimes called, is a curve of varying radius used to connect circular curves with tangents for the purpose of avoiding the shock and disagreeable lurch of trains, due to the instant change of direction and also to the sudden change from level to inclined track.
+The primary object of the transition curve, then, is to effect smooth riding when the train is entering or leaving a curve.
 
-	The generally accepted requirement for a proper transition curve is that the degree-of-curve
-	shall increase gradually and uniformly from the point of tangent until the degree of the main
-	curve is reached, and that the super-elevation shall increase uniformly from zero at the
-	tangent to the full amount at the connection with the main curve and yet have at any point
-	the appropriate super-elevation for the curvature. In addition to this, an acceptable transition
-	curve must be so simple that the field work may be easily and rapidly done, and should be so
-	flexible that it may be adjusted to meet the varied requirements of problems in location and
-	construction.
+	The generally accepted requirement for a proper transition curve is that the degree-of-curve shall increase gradually and uniformly from the point of tangent until the degree of the main curve is reached, and that the super-elevation shall increase uniformly from zero at the tangent to the full amount at the connection with the main curve and yet have at any point
+	the appropriate super-elevation for the curvature.
+In addition to this, an acceptable transition curve must be so simple that the field work may be easily and rapidly done, and should be so flexible that it may be adjusted to meet the varied requirements of problems in location and construction.
 \end{quotation}
 
-Given the expression of centripetal acceleration $V^{2} / R$, the obvious solution is to provide an easement curve whose curvature, $1/R$, increases linearly with the traveled distance.
-This geometry is an Euler spiral.
+Given the centripetal acceleration $a=v^2/R$, an obvious solution is to construct a curve whose curvature, $\kappa=1/R$, increases linearly with the traveled distance.
+This is the geometry of an Euler spiral \eqref{e:eulerSpiral}.
 
-Unaware of the solution of the geometry by Leonhard Euler, Rankine cited the cubic curve (a polynomial curve of degree 3), which is an approximation of the Euler spiral for small angular changes in the same way that a parabola is an approximation to a circular curve.
+Rankine did not know of the solution of the geometry problem by Leonhard Euler.
+Instead he proposed a cubic curve (a polynomial degree 3, $z(x)=ax^3+bx^2+cx+d$ with some adaptable coefficients $a,b,c,d$), an approximation of the exact solution for small angular changes.
+We can compare this to a parabola approximating a circle near a point.
 
-Marie Alfred Cornu (and later some civil engineers) also solved the calculus of Euler spirals independently.
-Euler spirals are now widely used in rail and highway engineering for providing a transition or an easement between a tangent and a horizontal circular curve.
+Marie Alfred Cornu (and later other civil engineers) also solved the problem of Euler spirals independently.
+Euler spirals are now-a-days widely used in railroad and highway construction, because they provide a smooth transition, i.e.~an easement, between a straight horizontal and an inclined track connected by a circular curve.
 

### 2019-03-17 draft.tex
final changes.

@@
 
-The Euler spiral, that is defined by a linear relationship between curvature and arc length, is a beautiful and elegant plane curve. Its underlying mathematical equation is most
-commonly known as the Fresnel integrals.
-However, the Fresnel integrals and Euler spiral are  two views of one and the same thing.
-In this paper, we focus on the Fresnel integrals and study its properties and useful applications.
-In optics, the illumination intensity at a point behind a straight edge is computed from the distance between two points on the Euler spiral.
-The Euler spiral also provides optimal curvature for train tracks between a straight run and an upcoming bend.
+The Euler spiral is a well known mathematical curve which can be constructed, e.g.~by peeling an orange along a spiral with a kitchen knife.
+Euler described it geometrically by a differential equation that sets the curvature linear to the arc length.
+On the other hand Fresnel integrals arise naturally in the mathematical description of Fresnel diffraction.
+We will study this in detail as a first application.
 
+We further reproduce the theorem that Fresnel integrals are the mathematical solutions of the Euler spiral.
+We also study another major application: railway transition curve construction where one tries to find a railway track than can be traveled smoothly even at higher velocities.
+We show that the transition curve construction has a simple solution in the Euler spiral.
+For practical purposes, we need to draw the Euler spiral or segments of it explicitly which can be done using the Fresnel integrals.
+
+In this sense we argue that the Euler spiral and the Fresnel integrals are two views of the same concept and are most fruitfully applied together.
 \end{abstract}
@@
 \subsection{Railway  Construction}
-An object traveling at speed $v$ on a circular path of radius $R$ experiences a centripetal acceleration $a$ as
+When a train travels at speed $v$ on a circular path of radius $R$ the passengers experience a centripetal acceleration $a$ as
 $$  a = v^2/R.
-$$ When a vehicle that travels on a straight path suddenly transitions to a circular path, then the acceleration sensed by the passengers suddenly changes from $0$ for the straight segment ($1/R=0$) to some positive value ($a>0$, because $1/R>0$).
-This sudden centripetal acceleration gives much discomfort for the driver as well as the passengers on the vehicle.
-The effect is small when, e.g.~the first trains traveled at quite low speeds, but becomes much stronger when the speed increases ($a\sim v^2$).
+$$ When the train travels on a straight (horizontal) line with constant speed there is no acceleration.
+However, in order to change the direction, we need to accelerate.
+The first solution that comes to mind is to connect the initial and final straight segments by a circle.
+But when the train passes this track at constant speed, the acceleration jumps from 0 for the straight segment ($1/R=0$) to some positive value ($a>0$, because $1/R>0$).
+This sudden change of acceleration can be much discomfort.
+The effect is small when, e.g.~the first trains, traveled at quite low speeds, but becomes much stronger when the speed increases ($a\sim v^2$).
 Therefore increased speeds of trains triggered the quest for better designed tracks.
+The problem is to find a transition curve from a straight tangential line segment to a circular segment.
+
+Different approaches were taken to this.
 According to \cite{Lev08}, Mr.
-Gravatt was the first one who choose a sine curve for the transition from a straight segment to a curve around the year of 1828.
-Later in 1842, William Froude proposed the use of an elastic curve in order to make the change of curvature more smooth.
-In 1880, Charles Crandall asks for priority for the ``true transition curve'' in the Railroad Gazette.
-The problem is officially on to Ellis Holbrook to be solved, however, Arthur Talbot was among the first to approach the problem mathematically.
-He describes the problem and his solution in the introduction to ``The Railway Transition Spiral'' \cite{Tal99} which we quote here for being pronounced:
+Gravatt was the first one who choose a sine curve for this transition around the year of 1828.
+Unlike a circle, the sine curve $y=\sin x$ has the curvature $\kappa=1/R=-\sin x/\left(1+(\cos x)^2\right)^{3/2}$ that changes continuously from $\kappa=0$ at $x=0$ to $\kappa=1$ at $x=\pi/2$ and back to $\kappa=0$ at $x=\pi$.
 
-\begin{quotation}
-	A transition curve, or easement curve, as it is sometimes called, is a curve of varying radius used to connect circular curves with tangents for the purpose of avoiding the shock and disagreeable lurch of trains, due to the instant change of direction and also to the sudden change from level to inclined track.
-The primary object of the transition curve, then, is to effect smooth riding when the train is entering or leaving a curve.
-
-	The generally accepted requirement for a proper transition curve is that the degree-of-curve shall increase gradually and uniformly from the point of tangent until the degree of the main curve is reached, and that the super-elevation shall increase uniformly from zero at the tangent to the full amount at the connection with the main curve and yet have at any point
-	the appropriate super-elevation for the curvature.
-In addition to this, an acceptable transition curve must be so simple that the field work may be easily and rapidly done, and should be so flexible that it may be adjusted to meet the varied requirements of problems in location and construction.
-\end{quotation}
+In 1880, Charles Crandall asked for priority for the ``true transition curve'' in the Railroad Gazette.
+The problem is officially on Ellis Holbrook to be solved, however, Arthur Talbot was among the first to approach the problem mathematically.
+He describes the problem and his solution in the introduction to ``The Railway Transition Spiral'' \cite{Tal99}.
 
@@
 \section{Conclusion}
-The Euler spiral is a well known mathematical curve which can be constructed by peeling an orange along a spiral with a kitchen knife.
-Fresnel integrals are the mathematical equations that describe the Euler spiral.
-In this paper, we mainly studied the properties of the Fresnel integrals and its two major applications: Fresnel Diffraction and railway transition curve construction.
+The Euler spiral is a well known mathematical curve which can be constructed, e.g.~by peeling an orange along a spiral with a kitchen knife.
+Euler described it geometrically by a differential equation that sets the curvature linear to the arc length.
+We showed that Fresnel integrals are the mathematical solutions of the Euler spiral.
+
+In this paper, we also studied two of its major applications: Fresnel diffraction in optics and a railway transition curve construction.
+While the former leads directly to the Fresnel integrals, it turns out that its practical evaluation relies fruitfully on the Euler spiral.
+
+We showed that the transition curve construction has a simple solution in the Euler spiral, because here the curvature changes linearly with the traveled distance (arc length).
+But for practical purposes, we need to draw the Euler spiral or segments of it explicitly which can be done using the Fresnel integrals.
+
+In this sense the Euler spiral and the Fresnel integrals are two views of the same concept and are most fruitfully applied together.
 
